%-------------------------
% Resume in Latex
% Author : Xinyue Ou 
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[3]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} &  \textit{\small #2} \\
    \end{tabular*}\vspace{-1pt}
    {\begin{itemize}[leftmargin=*]
    \small{#3}
    \end{itemize}}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Xinyue Ou} & Email : xinyue.ou@yahoo.com \\ 
   & Mobile : +1 858-405-4803\\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, San Diego}{La Jolla, CA}
      {Master of Science in Computer Science;  GPA: 3.80}{Sep. 2017 -- Dec. 2018}
    \resumeSubheading
      {Shanghai Jiao Tong University}{Shanghai, China}
      {Bachelor of Science in Electrical and Computer Engineering;  GPA: 3.89}{Sep. 2013 -- Aug. 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
	

    \resumeSubheading
      {Intel Asia-Pacific R\&D Center}{Shanghai, China}
      {Software Engineer Intern in BigDL Data Analytics}{Feb 2017 - July 2017}
      \resumeItemListStart
        \resumeItem{Neural Network Modules}
          {Used script language to efficiently port NN modules from Scala to Python.}
        \resumeItem{Memory Optimization}
          {Developed a shared-memory mechanism among modules saving half memory usage.}
        \resumeItem{Graph Model Converter}{ Built a graph converter in Scala converting machine learning models into graphs to accelerate the training of NN modules.}
      \resumeItemListEnd

    \resumeSubheading
      {Ailibi Medical Technology Co.}{Shanghai, China}
      {Software Engineer Intern}{Dec 2014 -- Feb 2015}
      \resumeItemListStart
        \resumeItem{Website Development}
          {Built the company's official website using HTML/CSS/JQuery.}
        \resumeItem{App Development Docs}
          {Documenting user requirements and specifications for the company's mobile app.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
       {Trition HTTP Server - C++}{April 2018 -- April 2018}
	   {Built a web server implementing  a subset of the HTTP/1.1 protocol specification using TCP socket programming.}
    
    \resumeProjectHeading
       {UCSD Class Schedule Calendar Generator - Javascript}{Feb 2018 -- Feb 2018}
	   {Designed a chrome extension that can generate a calendar file by parsing the web page of UCSD WebReg. }
  
    \resumeProjectHeading
       {RNN Music Generator - Python}{Feb 2018 -- Mar 2018}
       {Implemented a char-based generative LSTM model and trained it to “write” songs.}
  
	 \resumeProjectHeading
	   {XQuery Processor - Java, XML}{Feb 2018 - Mar 2018}
	   {Developed a simplified XQuery compiler with ANTLR and Java JDOM2. Implemented an optimized join operator to accelerate the join operation. Used gradle to set up the projecgt and  manage package dependency.}
  
	 \resumeProjectHeading{Gossip Membership Protocol - C++}{Nov 2017 -- Dec 2017}
	   {Implemented a gossip membership protocol in an emulated distributed system.}
    
  
	 \resumeProjectHeading
       {Multiprogramming Support for Nachos Kernel - Java}{Oct 2017 -- Nov 2017}
       {Designed a virtual memory management system that enables demand paging, lazy page loading and page swapping.
       Managed multithread programming using mutex, semaphore and conditional variable. 
       Implemented file-related and process-related system calls for Nachos kernel.}
    
   \resumeProjectHeading
	   {Passive Entry Passive Start Smart Key System - Java}{Jun 2017 -- Aug 2017}
	   { Built an Android App for motor vehicle key control based on Bluetooth Low Energy protocol. Developed with FastBLE framework and implemented noise filtering algorithm.}
         
  
  %  \resumeProjectHeading
  %       {Optimization of CT Image Reconstruction - MatLab}{Mar 2016 -- May 2016}
  %       {Used CGLS method to reconstruct medical image and optimized the computation speed by profiling. Built a GUI in MatLab which can inspect each slice in any given direction and the 3D image. }
  %  \resumeProjectHeading
  % 	     { Sign Language Translator Based on PIC32 - C}{Jun 2016 -- Aug 2016}
  % 	     {Constructed a sign language translator based on hand gestures captured by flex sensors and speed sensors. Developed a succinct data structure that makes use of small storage space of PIC32 to store signals and convert the matching to voice via VS1003 module}
	%  \resumeProjectHeading
	%      {Foreground Extraction Based on Optical Flow - C++}{Sep 2014 -- Mar 2015}
	%      {Used OpenCV library to compute intensive optical flow fields for each frame and discretized the vector fields.Tracked the foreground object based on the largest connected component, }

 
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
  \resumeItem{Languages}{: C++, Java, Python, Scala, Javascript, SQL. }\vspace{-5pt}
  \resumeItem{Tools}{: Git, TensorFlow, PyTorch, Docker, Gradle, Maven. }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
